Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-09-03 main.tex
Update on Overleaf.
some draft section

\begin{lemma}
    Let $\calT$ be a $n$-dimensional manifold triangulation and $V \in \Vertices(\calT)$ be an inner vertex.
    Then $\patch_{\calT}(V)$ is shellable. 
\end{lemma}
\begin{proof}
    Without loss of generality, $V$ is the origin. 
    Any ray starting at $V$ intersects at most one vertex of $\patch_{\calT}(V)$.
    We can also assume that all boundary vertices of $\patch_{\calT}(V)$ to be unit vectors,
    which does not affect shellability. 
    The simplicial boundary complex of $\calT$ is the boundary complex of a convex polytope,
    and is thus shellable~\cite[Theorem~8.12]{ziegler2012lectures}. 
\end{proof}

@@

        It is continuous and bi-Lipschitz due to Rademacher's theorem.

>>>>

\begin{lemma}\label{lemma:stars_are_shellable}
    Let $\calT$ be a $n$-dimensional manifold triangulation and $V \in \Vertices(\calT)$ be an inner vertex.
    Then $\patch_{\calT}(V)$ is shellable. 
\end{lemma}
\begin{proof}
    Without loss of generality, $V$ is the origin. 
    Any ray starting at $V$ intersects at most one vertex of $\patch_{\calT}(V)$.
    We can also assume that all boundary vertices of $\patch_{\calT}(V)$ to be unit vectors,
    which does not affect shellability. 
    The simplicial boundary complex of $\calT$ is the boundary complex of a convex polytope,
    and is thus shellable~\cite[Theorem~8.12]{ziegler2012lectures}. 
\end{proof}

@@

        \item 
        \color{red}
        We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
        We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
        After application of a piecewise linear Lipschitz mapping, 
        we can assume that $|\calK|$ is convex without loss of generality. 
        Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$.

        By an application of Rademacher's theorem, we conclude that $\calK$ is bi-Lipchitz. 
        \color{black}
